High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-03-31 notebooks/intro.qmd
no clue why quarto is bugging

```{julia}
X = table(permutedims(counterfactual_data.X))
y =  counterfactual_data.output_encoder.labels
conf_model = conformal_model(clf; method=:trainable_simple_inductive)
mach = machine(conf_model, X, y)
fit!(mach)
```

>>>>

```{julia}
X = table(permutedims(counterfactual_data.X))
y =  counterfactual_data.output_encoder.labels
conf_model = conformal_model(clf; method=:simple_inductive)
mach = machine(conf_model, X, y)
fit!(mach)
```
